Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-26 Dissertation/Thesis/tex/multivehicle.tex
edited 5.1.2 and inserted (unedited) 5.1.3

The robots unable to win the first auction are updated to reflect the expected impact of $R_{k^*}$. This robot is expected to modify the probabilistic occupancy grid map, which may significantly change the expected information gains and collision properties of candidate poses nearby $X^*_{k^*}$. The process of auctioning and modifying bids is repeated, removing the winning robot from consideration after each auction, until no robots remain. Between auctions, updating the map with expected measurements from auction-winning robots discourages the remaining robots from entering the same regions and capturing the same cells. As such, there is no need to consider the coverage overlap explicitly: it is avoided in a systematic way as increased coverage overlap would reduce the overall information gain.

@@

The first step between auctions is to modify the expected map information gain for efficient map coverage.  Once a robot wins a bid, the measurement ray expected values serve to update a temporary copy of $m_\text{2D}$, namely $m_\text{2D,copy}$, and those candidates located in a local neighborhood (twice the radius of a maximum sensor reading) of the winning candidate from the prior auction are recalculated, thereby coordinating total map information gain with auction-winning robots. Using the same local map notation from \refeqn{allEta} and \refeqn{Unnormalized} along a measurement ray, the expected measurement value is
\begin{align}
\label{eqn:ExpectedMeasRay}
\text{E}[z]=\sum_{k=1}^{n_{r}}\bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{m}}_j)\bigg\}P(\mathbf{m}_k)z_k,
\end{align}
where $z_k$ denotes the distance from the robot sensor to the $k$-th cell along the measurement ray. Then $\text{E}[z]$ is substituted into \refeqn{RayISMAnswer}--\refeqn{Unnormalized} to modify $m_\text{2D,copy}$, and expected map information gains are recomputed with \refeqn{ProbMeas} and \refeqn{expectedInfoGainRay}, while the bump function \refeqn{BumpFun} remains the same. In short, the expected changes of $m_\text{2D}$ are integrated into $m_\text{2D,copy}$ for expected information gain estimation between multiple vehicles.

The second step focusses on collision-avoidance between robots based on their proximity. Let $\rho_\text{max}>0$ be a fixed maximum radius to consider collision-avoidance and $\rho_{i,c}\geq0$ be the Euclidean distance from the $i$-th already-assigned pose $X^*_i$ to the $c$-th candidate pose $X_c$, i.e.,
\begin{align}
\rho_{i,c}&=\norm{x^*_i-x_c},
\end{align}
where $x^*_i$ and $x_c$ are the pose locations of $X^*_i$ and $X_c$, respectively. Then the collision-avoidance factor for the $k$-th robot such that $R_k\notin\mathcal W$ is,
\begin{align}
\label{eqn:CollisionAvoidanceAmongRobots}
\mathbf C(X_c)&=
\begin{cases}
    \prod_{i|\mathcal{R}_i\in\mathcal W} \left(\frac{\rho_{i,c}}{\rho_\text{max}}\right)^2,		& \text{if }\rho_{i,c}<\rho_\text{max},\\
    1,              				& \text{otherwise},
\end{cases}
\end{align}
where this product serves to decrease the value of bids for candidate poses in close proximity with already-assigned poses to avoid collisions between robots. The multi-vehicle objective function for the $k$-th robot accounting for collision-avoidance is
\begin{align}
\label{eqn:CandidateBidMulti}
\text{Obj}_\text{multi}(X_k,X_c,m_\text{2D,copy})
=\mathbf C(X_c)\mathcal B(d(X_k,X_c,m_\text{2D}))\mathcal I(X_{c},m_\text{2D,copy}),
\end{align}
where its optimal pose during this auction is
\begin{align}
\label{eqn:OptPoseMulti}
X^*_{k}=\argmax_{X_c}\text{Obj}_\text{multi}&(X_k,X_c,m_\text{2D,copy}),
\end{align}
where $\text{Obj}_\text{multi}(X^*_k,X_c,m_\text{2D,copy})$ is the bid for the $k$-th robot.
Optimal pose selection and bidding is repeated for all robots not belonging to $\mathcal W$. The largest bid among these wins the auction and is tasked with moving to the associated pose candidate, and then this robot is included with $\mathcal W$ to avoid further consideration. Completing $n_R$ auctions produces $\mathcal X^*$.

@@

>>>>

The robots unable to win the first auction are updated to reflect the expected impact from the first robot traveling to optimal pose $X^*_{k^*}$.
This robot is expected to modify the probabilistic occupancy grid map, which may significantly change the expected information gains and collision properties of candidate poses nearby. The process of auctioning and modifying bids is repeated, removing the winning robot from consideration after each auction, until no robots remain. Between auctions, updating the map with expected measurements from auction-winning robots discourages the remaining robots from entering the same regions and capturing the same cells. As such, there is no need to consider the coverage overlap explicitly as in~\cite{SimApfBurFoxMooThrYou00}; instead coverage overlap is avoided in a systematic way as increased coverage overlap would reduce the overall information gain.

@@

The first step between auctions is to modify the expected map information gain for efficient map coverage.  Once a robot wins a bid, the measurement ray expected values serve to update a temporary copy of $m_\text{2D}$, namely $m_\text{2D,copy}$, and those candidates located in a local neighborhood (twice the radius of a maximum sensor reading) of the winning candidate from the prior auction are recalculated, thereby coordinating total map information gain with auction-winning robots. Using the same local map notation from \refeqn{allEta} and \refeqn{Unnormalized} along a measurement ray, the expected measurement value is
\begin{align}
\label{eqn:ExpectedMeasRay}
\text{E}[z]=\sum_{k=1}^{n_{r}}\bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{m}}_j)\bigg\}P(\mathbf{m}_k)z_k,
\end{align}
where $z_k$ denotes the distance from the robot sensor to the $k$-th cell along the measurement ray. Then $\text{E}[z]$ is substituted into \refeqn{RayISMAnswer}--\refeqn{allEta} to modify $m_\text{2D,copy}$, and expected map information gains are recomputed with \refeqn{ProbMeas} and \refeqn{expectedInfoGainRay}, while the bump function \refeqn{BumpFun} remains the same. In short, the expected changes of $m_\text{2D}$ are integrated into $m_\text{2D,copy}$ for expected information gain estimation between multiple vehicles.

% TODO: make sure find/replace of:
% \refeqn{RayISMAnswer}--\refeqn{Unnormalized}
%  \refeqn{RayISMAnswer}--\refeqn{allEta}

The second step focusses on collision-avoidance between robots based on their proximity. Let $\rho_\text{max}>0$ be a fixed maximum radius to consider collision-avoidance and $\rho_{i,c}\geq0$ be the Euclidean distance from the $i$-th already-assigned pose $X^*_i$ to the $c$-th candidate pose $X_c$, i.e.,
\begin{align}
\rho_{i,c}&=\norm{x^*_i-x_c},
\end{align}
where $x^*_i$ and $x_c$ are the pose locations of $X^*_i$ and $X_c$, respectively. Then the collision-avoidance factor for the $k$-th robot such that $R_k\notin\mathcal W$ is,
\begin{align}
\label{eqn:CollisionAvoidanceAmongRobots}
\mathbf C(X_c)&=
\begin{cases}
    \prod_{i|\mathcal{R}_i\in\mathcal W} \left(\frac{\rho_{i,c}}{\rho_\text{max}}\right)^2,		& \text{if }\rho_{i,c}<\rho_\text{max},\\
    1,              				& \text{otherwise},
\end{cases}
\end{align}
where this product serves to decrease the value of bids for candidate poses in close proximity with already-assigned poses to avoid collisions between robots. The multi-vehicle objective function for the $k$-th robot accounting for collision-avoidance is
\begin{align}
\label{eqn:CandidateBidMulti}
\text{Obj}_\text{multi}(X_k,X_c,m_\text{2D,copy})
=\mathbf C(X_c)\mathcal B(d(X_k,X_c,m_\text{2D}))\mathcal I(X_{c},m_\text{2D,copy}),
\end{align}
where its optimal pose during this auction is
\begin{align}
\label{eqn:OptPoseMulti}
X^*_{k}=\argmax_{X_c}\text{Obj}_\text{multi}&(X_k,X_c,m_\text{2D,copy}),
\end{align}
such that $\text{Obj}_\text{multi}(X^*_k,X_c,m_\text{2D,copy})$ is the bid for the $k$-th robot.
Optimal pose selection and bidding is repeated for all robots not belonging to $\mathcal W$. The largest bid among these wins the auction and is tasked with moving to the associated pose candidate, and then this robot is included with $\mathcal W$ to avoid further consideration. Completing $n_R$ auctions produces the set of coordinated poses $\mathcal X^*$.

@@

This algorithm is further aided by following a receding horizon framework for improved information gain maximizations and collision-avoidance with dynamic obstacles and other robots. A receding horizon simply repeats the autonomous exploration steps as quickly as possible over a finite time period, frequently before a robot reaches its desired pose. Since exploration optimizations can only occur during exploration updates, a receding horizon maximizes the rate at which these updates occur. These updates require time for computation, over which the robot can move $d_\text{opt}$, used to optimize the robot travel distances with \refeqn{BumpFun}. Hence, the receding horizon framework serves to repeat optimizations as quickly as possible with maximal robotic movement while exploring a changing occupancy grid.

Furthermore, a receding horizon framework enhances autonomous exploration in two other ways. First, the occupancy grid map is constantly updated while a robot traverses a trajectory, so the expected information gains change as well. Since the bids depend on the occupancy grid, $\mathcal X^*$ is updated accordingly. This prevents robots from completing trajectories that have become unnecessary as new terrain becomes captured. Second, the receding horizon prevents robots from colliding with each other when they become too close together (e.g., crossing paths, traversing a tight passage) or other moving obstacles (e.g., a human). The cost map for each robot is updated, and the location of other robots are considered as collision-prone space. Hence, the robot trajectories become better separated due to rapid updates of the cost maps with the receding horizon.
